Deep learning for geophysics

### 2023-10-11 manuscript.tex
Add acknowledgements

\directlua{pdf.setminorversion(6)}
\documentclass[12pt,a4paper,notitlepage]{report} %,openright,twoside scrbook
% \includeonly{}
\usepackage{thesisstyle}
\addbibresource{bib/PhD.bib}
\begin{document}

@@

\newpage{}
\addsec{Acknowledgements}
\dots{}

This research was supported by a Rio Tinto Iron Ore PhD Scholarship.

\vfill{}
\epigraph{\emph{But all collected data had yet to be completely correlated and put together in all possible relationships.}}{Isaac Asimov}

>>>>

\directlua{pdf.setminorversion(6)}
\documentclass[12pt,a4paper,notitlepage]{report} %,openright,twoside scrbook
% \includeonly{}
\usepackage{thesisstyle}
\addbibresource{bib/PhD.bib}

\begin{document}

@@

\newpage{}
\addsec{Acknowledgements}

I wish to thank a great number of people who have contributed to my ongoing development.
First, to my supervisors:
EJ, for bringing together a team of talented and friendly geodata scientists, and caring deeply for them all.
Tom, who set a high bar with his PhD and immediately set about raising his students to the same level.
Daniel, for the meticulous, concise, and actionable reviews and suggestions.
Naveed, whose perspective was invaluable.
Andie, Dale, and Robert, and the rest of my family in NSW --- I didn't get to visit as much as I had originally planned in 2019, but we made the most of it! Thanks for the support and encouragement, and imparting all the passions of rocks, computers, and tinkering that I have today.
Tasman, for being a good friend and inspirational colleague for most of my academic career --- looking forward to sharing a project again sometime, somewhere in the future!
Lu, for sharing your incredible amount of geophysics knowledge, incredible cooking, and love of tennis with me.
Matilda, for being a wonderful friend and the best housemate --- Thanks for being silly with me.
My first floor colleagues and fellow tech geeks, Daniel, David, Chris, Minh, and Peter --- Your friendship and knowledge has been a wonderful environment to grow as a geodata scientist in.
And all my SES, CET, and friends beyond: Alex, Anne, Ben, France, Jackson, Jules, Kailah, Lauren, Lauri, Liam, Lilly, Maddie, Maria, Malvina, Nicolas, Ravi, Sean, Sumail, Vickie, and Ze --- Thank you for years of lunches, dinners, beaches, rock climbing, yoga, and all the opportunities to talk rocks that I've been missing.
And to all the teachers throughout my life, both professional and incidental: Thank you.

I love you all.

\bigskip
\noindent This research was supported by a Rio Tinto Iron Ore PhD Scholarship.

\vfill{}
\epigraph{
    \textit{All collected data had come to a final end. Nothing was left to be collected.}

    \smallskip
    \textit{But all collected data had yet to be completely correlated and put together in all possible relationships.}}{Isaac Asimov}
